%\nocite{*} % Show all Bib-entries
\begin{thebibliography}{9}

\bibitem{J1} André Joyal, \emph{Une théorie combinatoire des séries
formelles}, Adv. Math 42 (1981), 1–82

\bibitem{J2} André Joyal, \emph{Foncteurs analytiques et espèces des
structures}, in Combinatoire Énumérative, Lecture Notes in Mathematics 1234, Springer,
Berlin, (1986), pp. 126–159

\bibitem{BergTrees} F. Bergeron, Gilbert Labelle, Pierre LeRoux,
\emph{Combinatorial Species and Tree-Like Structures}, Cambridge University Press, (1998)

\bibitem{BergH} N. Bergeron, P. Choquette,
\emph{Hyperoctahedral species}, Sém. Lothar. Combin. 61A (2009/10), доступно на
\url{http://arxiv.org/abs/0810.4089}

\bibitem{Cubic} Hetyei, Gábor, Labelle, Gilbert,
Leroux, Pierre \emph{Cubical species and nonassociative algebras} Adv. in Appl.
Math. (1998), no. 3

\bibitem{Mac1} I. G. Macdonald, \emph{Polynomial functors and wreath
products}, J. Pure Appl. Algebra, 18(2):173–204, (1980)

\bibitem{Mac2} I. G. Macdonald, \emph{Symmetric functions and Hall polynomials},
Oxford Mathematical Monographs.
The Clarendon Press Oxford University Press, New York, second edition, (1995)

\bibitem{Day} nLab, \emph{Day convolution},
\url{http://nlab.mathforge.org/nlab/show/Day+convolution}

\bibitem{Durov} Н. В. Дуров, \emph{Классифицирующие вектоиды и классы операд},
Санкт-Петербургское отделение Математического института им. В. А. Стеклова РАН,
Санкт-Петербург, Россия (2009), доступно (английский) на
\url{http://arxiv.org/abs/1105.3114}

\bibitem{doldkan} Akhil Mathew, \emph{The Dold-Kan correspondence between
simplicial abelian groups and chain complexes}, Expository writings (2011),
доступно на \url{http://people.fas.harvard.edu/~amathew/doldkan.pdf}

\bibitem{travis} Leopold Travis, \emph{Graphical Enumeration: A
Species-Theoretic Approach}, Dissertation (1999), доступно на
\url{http://arxiv.org/pdf/math/9811127v1.pdf}

\bibitem{lambda} Anthony Mendes, Jeffrey Remmel, Jennifer Wagner,
\emph{A $\lambda$-ring Frobenius Characteristic for $G \wr S_n$}, The electronic
journal of combinatorics 11 (2004), \#R56, доступно на 
\url{http://www.combinatorics.org/ojs/index.php/eljc/article/download/v11i1r56/pdf}

\bibitem{stack} Задача обсуждается на
\url{http://math.stackexchange.com/questions/5697/coloring-the-faces-of-a-hypercube}

\end{thebibliography}